---
title: "data"
author: "Madeleine A"
date: 'Spring 2022'
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
require(tigerstats)
```


```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
favstats(my1000)
```

According to this density plot we can see that there are two peaks and they look about the same size, which means it is bimodel. This means there is bimodel distribution and both values in this data have the highest frequency. The mean is. 49.1 and the standarddeviation is 42.2.



```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
favstats(x.avg)
```
According to this plot, we can see that there are 3 peaks and the middle peak being the highest one. The mean is 48.5 and the standard deviation is 29.5. When we actually do the calculation, we get 


```{r}
numb = 3
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 3")
favstats(x.avg)
```
In the. plot, we can see that there are four peaks. The mean is. 50.6 and the standard deviation is 23.8 When we actually do the calculation, we get 21.87 which is very close to the standard deviation.

```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
favstats(x.avg)
```
Here the mean is 50.44 and the sd is 20.61. 


```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
favstats(x.avg)
```

```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
favstats(x.avg)
```

Here we can see that we have one peak. The value of the mean is 50.2 and the value of the standard deviation is 10.6. The calculated value is 10.55 which is super close to 10.6.




```{r}
numb = 25
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 25")
favstats(x.avg)
```

In this plot, we can see that we have one peak which indicates normal distribution. The mean of this sample is 50.70 and the sd is about 8.3. When we do the actual calculation, we get a value of 8.44 which is right along the lines of 8.28.



```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
favstats(x.avg)
```
Here we can see that there is only one peak now which indicates normal distribution. The mean is 50.43 and the SD is 7.1. When we do the actual calculation,(standard deviation of the very first sample divided by the square root of 36 = 6) we get a value of 7.045 which is very very close to the actual standard deviation ~ 7.1





In conclusion, after analyzing each sample, we can verify that we have normal distribution. The central limit theorem was very close or almost the same to the normal distribution.